Stochastic Variance Reduced Policy Gradient

### 2018-02-04 svrpg.tex
added opening to proofs appendix

\section{Proofs}\label{app:proofs}

>>>>

\section{Proofs}\label{app:proofs}
In this Appendix we prove all the claims made in the paper, with the primary objective of proving Theorem \ref{theo:convergence}. Our proof is adapted from the one of Theorem 2 from \cite{reddi2016stochastic} and has a very similar structure, but with all the additional challenges and assumptions described in Section \ref{sec:conv}.
